Secure Composition of Robust and Optimising Compilers

### 2023-07-05 popl/main.tex
some todos for the rest of 2.1

As described earlier, partial programs cannot be executed, because they lack definitions and, thus, get stuck.
{\em Linking} ($\link{\progvar[_{1}]}{\progvar[_{2}]}$) syntactic descriptions $\progvar[_{1}],\progvar[_{2}]$ can give rise to a whole program.
Note that linking is not defined on programs, but merely on their syntactic descriptions, since programs contain dynamic state.
However, for convenience, linking of programs $\runtimetermvar[_{1}],\runtimetermvar[_{2}]$ shall be defined if both $\runtimetermvar[_{1}]$ and $\runtimetermvar[_{2}]$ have an initial dynamic state.
As typically done in a secure compilation context~\cite{abate2019jour}, this paper also assumes that programs are the result of linking a {\em context} ($\ctx$) and a {\em component} ($\comp$), which are just any syntactic description.
The component part of a whole program is the main object of interest and thus a known syntactic description.
In contrast, the context is usually arbitrary and thus has the role of an active {\em attacker} that can interact with the component by means of whatever features the programming language has.
The following extends on \Thmref{def:propsat} to cover {\em robustness} and exploits this interaction between the context and the component:

\begin{definition}[Robust Satisfaction]\label{def:proprsat}
  A program $\runtimetermvar$ robustly satisfies $\pi$ ($\rsat{\runtimetermvar}{\pi}$) iff for any partial program $\contextvar$ it holds that $\sat{\link{\contextvar}{\runtimetermvar}}{\pi}$.
\end{definition}
\subsection{Secure Compilers}\label{subsec:bg:rtp}

>>>>

As described earlier, partial programs cannot be executed \MP{not true anymore, need to define the notion of partial programs} , because they lack definitions and, thus, get stuck.
{\em Linking} ($\link{\progvar[_{1}]}{\progvar[_{2}]}$) syntactic descriptions $\progvar[_{1}],\progvar[_{2}]$ can give rise to a whole program.
Note that linking is not defined on programs, but merely on their syntactic descriptions, since programs contain dynamic state.\MP{ not terminology i really want to use, nor is defined}
However, for convenience, linking of programs $\runtimetermvar[_{1}],\runtimetermvar[_{2}]$ shall be defined if both $\runtimetermvar[_{1}]$ and $\runtimetermvar[_{2}]$ have an initial dynamic state.
As typically done in a secure compilation context~\cite{abate2019jour}, \MP{others do this too, parametricity results e.g.} this paper also assumes that programs are the result of linking a {\em context} ($\ctx$) and a {\em component} ($\comp$), which are just any syntactic description.
\MP{just introduce the notion of contexts}
The component part of a whole program is the main object of interest and thus a known syntactic description.
In contrast, the context is usually arbitrary and thus has the role of an active {\em attacker} that can interact with the component by means of whatever features the programming language has.
\MP{and say the semantics is expected (passive, hah) to differentiate between prg and ctx}
The following extends on \Thmref{def:propsat} to cover {\em robustness} and exploits this interaction between the context and the component:
\MPin{missing: the context is an attacker! now, unlike before, we security property satisfaction with a clear active attacker}

\begin{definition}[Robust Satisfaction]\label{def:proprsat}
  A program $\runtimetermvar$ robustly satisfies $\pi$ ($\rsat{\runtimetermvar}{\pi}$) iff for any partial program $\contextvar$ it holds that $\sat{\link{\contextvar}{\runtimetermvar}}{\pi}$.
\end{definition}

\MPin{
	classes?
}
\subsection{Secure Compilers}\label{subsec:bg:rtp}
